\documentclass{article}
\usepackage{amsmath}
\begin{document}
\title{Exercises of Mining of Massive Datasets}
\author{Qiongsi Wu}
\maketitle
\section{Data Mining}
\subsection{Exercise 1.2.1}
This looks easy. We can do exactly the same as in the example. We are looking for the number of suspected pairs, which equals the number of pairs of people, times the number of "three days" triples, and the probability that any two people are meeting at a given hotel for three days. 

The number of pairs of people is given by ${n \choose 2}$, where n is the size of the total population, which is 2 billion. Using the approximation in the text, the number of pairs is
${2\times10^{9} \choose 2} \approx {{4\times10^{18}}\over2} = 2\times10^{18}$

The number of "three day" triples equals ${2000 \choose 3}$ which equals 1,331,334,000. This is about 1.3 billion, or $1.33\times10^9$. 

The probability of two people both visiting one hotel on any given day is 0.0001. The chance they are visiting the same hotel on the same day is 0.0001 divide by the number of hotels (200,000) which gives $5\times10^{-10}$. 

Why can we  divide the probability of two people visiting a hotel on the same day by the number of hotels to get the probability that they will visit the same hotel on the same day?  What is the probability that they are going to go to the same hotel, given that both of them are going? 

The probability of person one visit a particular hotel is $1\over n$ where n is the number of hotels. The probability of both of them going to the same hotel is $({1\over n})^2$. Meanwhile, there are $n$ hotels to choose from. Hence the probability of both person visiting a same hotel is $({1\over n})^2\times n = {1\over n}$.

Then, the probability of two people visiting the same hotels on three different days is $({5\times10^{-10}})^3 = 1.25\times10^{-28}$.  

Finally, the answer to the question is the product
\[({2\times10^{18}})\times({1.33\times10^9})\times({1.25\times10^{-28}}) = 3.325\times10^{-1} = 0.3325\]

Wow, this seem to imply the number of the possible pairs of people who exhibit this pattern is really small! 

\end{document}